### 2013-02-14 doc/xps2013/proposal.tex
oskin crap

Oskin has... {\bf MARK PUT YOUR STUFF HERE.}

>>>>

Oskin has explored a wide variety of architectural mechanisms for improving application performance, most notably intelligent memory~\cite{activepages} and dataflow computing~\cite{wavescalar-micro, wavescalar-isca}.  He has developed novel evaluation techniques~\cite{hls} that enable efficient design space exploration of complex superscalar processors.  His past work has included runtime systems for GPU-based computing~\cite{oskin-gpu}, application specific processor design~\cite{sherpa} and polymorphic on-chip networks~\cite{polynetworks}.  He has also explored several architectural design options for quantum computers~\cite{quantum-isca03, quantum-isca05, quantum-isca08}.  Finally he developed mechanisms to make parallel systems more deterministic and easier to program~\cite{dmp}.  His most recent work is focused on the work described in this proposal~\cite{Nelson:hotpar2011}, which is to make irregular computations efficient on commodity hardware.
